%-------------------------
% Resume in LaTeX
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage[normalem]{ulem}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\large\normalfont\uppercase
}{}{0em}{}[\titlerule \vspace{-4pt}]




% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands for compact bullet points
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, topsep=2pt, partopsep=0pt, parsep=0pt, itemsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Nidhish Jain} \\ \vspace{1pt}
    International Institute of Information Technology, Hyderabad \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 8103052776 ~ \href{mailto:nidhish.jain@students.iiit.ac.in}{\raisebox{-0.2\height}\faEnvelope\  \underline{nidhish.jain@students.iiit.ac.in}} ~ 
    \href{https://www.linkedin.com/in/nidhish-jain-43ab52280/}{\raisebox{-0.2\height}\faLinkedin\ \underline{Nidhish Jain}}  ~
    \href{https://github.com/Nidhishj}{\raisebox{-0.2\height}\faGithub\ \underline{Nidhishj}}
\end{center}

\section*{Education}
\textbf{International Institute of Information Technology, Hyderabad} \hfill \textit{2023 -- Present} \\
\small{\textit{B.Tech in Computer Science and Engineering} \hfill CGPA: 8.78}

\section*{Experience}
\textbf{Undergraduate Researcher} \hfill \textit{May 2025 -- Present} \\
\small{\textit{CVIT, IIITH} \hfill Hyderabad, India} \\
\resumeItemListStart
\resumeItem{Collaborating with Prof. Jayanthi Sivaswamy on medical imaging and segmentation research.}
\resumeItem{Developing a multi-modal image segmentation model using deep learning to improve anatomical structure delineation.}
\resumeItemListEnd
\vspace{8pt}
\textbf{Software Development Intern $|$\href{https://github.com/Nidhishj/Asset_Management_System}{ GitHub}} \hfill \textit{Jan 2025 -- May 2025} \\
\small{\textit{Eklavya Foundation} \hfill Remote / Hyderabad, India} \\
\resumeItemListStart
\resumeItem{Developed a Smart Asset Management System using MERN stack to manage organizational assets, projects and users.}
\resumeItem{Enhanced the system with real-time form validation, database export facility and automated asset report generation.}
\resumeItemListEnd

\section{Projects}
\textbf{Distributed Network File System (NFS)} $|$ \href{https://github.com/Nidhishj/NFS}{GitHub} - \small{\textit{C, Threads, TCP Networking}} \\
\resumeItemListStart
\resumeItem{Designed scalable distributed NFS architecture with dedicated naming server, storage servers, and clients over TCP.}
\resumeItem{Implemented concurrent file operations with multi-threading, synchronization primitives, and fault-tolerant data replication.}
\vspace{-11pt}
\resumeItem{Enhanced path resolution performance by leveraging trie and hash map; added support for audio file streaming.}
\resumeItemListEnd
\vspace{8pt}

\textbf{Crowd Detection App} $|$ \href{https://github.com/Nidhishj/ESW-PROJECT}{GitHub} - \small{\textit{Kotlin, OpenCV, TFLite, Android, QIDK}} \\
\resumeItemListStart
\resumeItem{Created an Android app for real-time crowd and emotion detection leveraging QIDK kits computing power.}
\vspace{2pt}

\resumeItem{Incorporated multiple crowd detection models to optimize battery usage on QIDK kits.}
\vspace{2pt}

\resumeItem{Trained an emotion detection model and merged it with the crowd detection model for real-time analysis.}
\resumeItemListEnd
\vspace{8pt}

% \textbf{Buy-Sell-IIITH} $|$ \href{https://github.com/Nidhishj/Buy-Sell-IIITH/tree/main}{GitHub} - \small{\textit{MongoDB, Express, React, Node.js}} \\
% \resumeItemListStart
% \resumeItem{Developed campus marketplace platform with item listing, browsing and JWT authentication.}
% \resumeItem{Enhanced user experience by integrating an AI chatbot for real-time assistance and engagement.}
% \resumeItemListEnd
% \vspace{8pt}

\textbf{LoRAQ} $|$ \href{https://github.com/Nidhishj/LoRAQ}{GitHub} - \small{\textit{Python, Reinforcement Learning, NumPy}} \\
\resumeItemListStart
\resumeItem{Built an RL-based framework for low-rank matrix approximation, reducing computation time while maintaining accuracy.}
\vspace{-10pt}
\resumeItem{Applied DQN, A2C, and hybrid methods to accelerate approximation by up to 50\% on GPUs.}
\vspace{2pt}
\resumeItem{Incorporated adaptive strategies and early stopping to reduce training time by over 30\% with minimal error increase.}
\resumeItemListEnd
\vspace{8pt}

\textbf{CShell} $|$ \href{https://github.com/Nidhishj/C-shell}{GitHub} - \small{\textit{C, Unix, Shell Design}} \\
\resumeItemListStart
\resumeItem{Built a modular Unix-like shell in C with job control, signals, I/O redirection, pipelines and robust process management.}
\vspace{2pt}
\resumeItem{Implemented 10+ commands along with history, aliases, error handling and foreground/background process control.}
\resumeItemListEnd

% \section{Achievements \& Extracurriculars}
% \resumeItemListStart
% \resumeItem{\textbf{Merit List Award:} Recipient for three semesters at IIIT-H.}\hfill\textit{2023-2025}
% % \vspace{2.33pt}
% \resumeItem{\textbf{ICPC India Prelims:} Secured team rank of 129 out of 2930 teams which participated.} \hfill\href{https://indiaicpc.in/ranklist.html}{\textit{2025-ranklist}}
% % \vspace{2.33pt}
% \resumeItem{\textbf{Codeforces:} Rated Specialist with Max Rating of 1517.} \hfill\href{https://codeforces.com/profile/nidhissssssssssssh}{\textit{nidhissssssssssssh}}
% % \vspace{2.33pt}

% \resumeItem{\textbf{JEE Mains:} Secured All India Rank 1256 (99.899 percentile) among 1.2 million candidates.}\hfill\textit{2023}
% % \vspace{2.33pt}

% \resumeItem{\textbf{JEE Advanced:} Achieved All India Rank 2698 among 150,000 candidates.}\hfill{\textit{2023}}
% % \vspace{2.33pt}

% \resumeItem{\textbf{KVPY-SA:} Secured All India Rank 1250, Merit List Holder.}\hfill{\textit{2022}}
% % \vspace{2.33pt}

% \resumeItem{\textbf{NTSE Scholar:} Qualified both stages (State and National) of the National Talent Search Examination.}\hfill{\textit{2021}}
% % \vspace{2.33pt}
% \resumeItem{\textbf{Teaching Assistant, Computer Programming:} Problem and contest design, tutorials, and evaluation for 150 students.}
% % \vspace{2.33pt}
% \resumeItem{\textbf{Marketing Head, Gaming Club, IIIT-H:} Leading 10-member team, managing social media \& organizing events.}
% \resumeItemListEnd
\section{Achievements \& Extracurriculars}
\resumeItemListStart

\resumeItem{\textbf{Merit List Award:} Recipient for three semesters at IIIT-H. \hfill \textit{2023--2025}}

\resumeItem{\textbf{ICPC India Prelims:} Secured team rank of 129 out of 2930 teams which participated.
\hfill \href{https://indiaicpc.in/ranklist.html}{\textit{2025 Ranklist}}}

\resumeItem{\textbf{Codeforces:} Rated Specialist with Max Rating of 1556.
\hfill \href{https://codeforces.com/profile/nidhissssssssssssh}{\textit{nidhissssssssssssh}}}
 
\resumeItem{\textbf{JEE Mains:} Secured All India Rank 1256 (99.899 percentile) among 1.2 million candidates.
\hfill \textit{2023}}

\resumeItem{\textbf{JEE Advanced:} Achieved All India Rank 2698 among 150,000 candidates.
\hfill \textit{2023}}

\resumeItem{\textbf{KVPY-SA:} Secured All India Rank 1250, Merit List Holder.
\hfill \textit{2022}}

\resumeItem{\textbf{NTSE Scholar:} Qualified both stages (State and National) of the National Talent Search Examination.
\hfill \textit{2021}}

% \resumeItem{\textbf{Teaching Assistant, Computer Programming:} Problem and contest design, tutorials, and evaluation for 150 students.}\resumeItem{\textbf{Marketing Head, Gaming Club, IIIT-H:} Leading a 10-member team, managing social media \& organizing events.}

\resumeItemListEnd

\section{Technical Skills}
\small{
\textbf{Languages:} Python, C, C++, JavaScript, HTML/CSS, SQL\\
    \textbf{Technologies/Frameworks:} Linux, Git, React, Express, MongoDB, Node.js, Flask, NumPy, Pandas, OpenCV, PyTorch\\
}
\vspace{-5pt}
\section{Relevant Coursework}
\small{
\textbf{Computer Science:} Data Structures \& Algorithms, Operating Systems \& Networks, Algorithm Analysis \& Design, Computer System Organization, Automata Theory, Databases and Applications,Machine Learning, Statistical Methods in AI \\
\textbf{Development:} Introduction to Software Systems, Internet of Things, Design \& Analysis of Software Systems \\
\textbf{Mathematics:} Linear Algebra, Real Analysis, Probability and Statistics, Discrete Structures, Numerical Algorithms
}

\end{document}